---
title: "COVID 19 Data Exploration"
author: "Voltaire Jay Recto"
date: "7/10/2021"
output: html_document
---

## COVID 19 Data Exploration

Exploring COVID 19 data using R Studio Cloud.

Data source: https://ourworldindata.org/covid-deaths

Installing tidyverse

```{r}
install.packages("tidyverse")
library(tidyverse)
```

Importing data to R

```{r}
covid_data <- read.csv("owid-covid-data.csv")
```

Previewing data

```{r}
glimpse(covid_data)
```

```{r}
colnames(covid_data)
```

Creating new dataframe with selected columns

```{r}
covid_cases <- select(covid_data, location, date, total_cases, new_cases, total_deaths, population)
```

Reviewing new dataframe

```{r}
glimpse(covid_cases)
```

Adding new column for infection rate

```{r}
covid_cases <- mutate(covid_cases, infected_percent = total_cases/population*100)
```

Adding another column, this time for death rate

```{r}
covid_cases <- mutate(covid_cases, death_percent = total_deaths/total_cases*100)
```

Reviewing updated data

```{r}
glimpse(covid_cases)
```

Created new dataframe to filter only data from July 1

```{r}
covid_cases_701 <- filter(covid_cases, date=="2021-07-01")
```

In order to plot only the highest % countries, we are creating new dataframes for plotting.

```{r}
covid_cases_inf <- filter(covid_cases_701, infected_percent>=10)
```

```{r}
covid_cases_death <- filter(covid_cases_701, death_percent>=5)
```

Installing ggplot2 in order to plot graphs

```{r}
install.packages('ggplot2')
library(ggplot2)
```

Creating plot for infection rate

```{r}
ggplot(data = covid_cases_inf) +
  geom_col(mapping = aes(x = location, y = infected_percent)) +
  labs(title="Countries with Highest Infection",
     caption=paste0("As of July 1, 2021"),
     x="Location",
     y="Infection Percentage") +
  theme(axis.text.x=element_text(angle = 90, hjust = 0))
```

Creating plot for death rate

```{r}
ggplot(data = covid_cases_death) +
  geom_col(mapping = aes(x = location, y = death_percent)) +
  labs(title="Countries with Highest Death Rate",
       caption=paste0("As of July 1, 2021"),
       x="Location",
       y="Death Percentage") +
  theme(axis.text.x=element_text(angle = 90, hjust = 0))
```

